Part B-1

### 2025-04-28 msca-pf-part-b1-template.tex
feat: rework helper environments and showcase cv
feat: add latex labels to each section
feat: bump year to 2025
feat: some more updates from the 4.1 changes

@@

@@

\section{Excellence \mscatag{REL-EVA-RE}}

\subsection{
    Quality and pertinence of the project's research and innovation objectives
    (and the extent to which they are ambitious, and go beyond the state of the art)}

@@

\subsection{
    Soundness of the proposed methodology
    (including interdisciplinary approaches, consideration of the gender
    dimension and other diversity aspects if relevant for the research project,
    and the quality of open science practices)}

@@

    \footnotetext{Interdisciplinarity means the integration of information, data,
    techniques, tools, perspectives, concepts or theories from two or more
    scientific disciplines.}

@@

        \item  Sex, gender and diversity analysis refers to biological
        characteristics and social/cultural factors respectively. For guidance on
        methods of sex / gender analysis and the issues to be taken into account,
        please refer to
        \href{https://ec.europa.eu/info/news/gendered-innovations-2-2020-nov-24_en}{this page}.

        \item If you plan to use, develop and/or deploy artificial intelligence
        (AI) based systems and/or techniques you must demonstrate their technical
        robustness. AI-based systems or techniques should be, or be developed to
        become:

        \begin{itemize}
            \item technically robust, accurate and reproducible, and able to
            deal with and inform about possible failures, inaccuracies and
            errors, proportionate to the assessed risk they pose,

            \item socially robust, in that they duly consider the context and
            environment in which they operate,

            \item reliable and function as intended, minimizing unintentional
            and unexpected harm, preventing unacceptable harm and safeguarding
            the physical and mental integrity of humans,

            \item able to provide a suitable explanation of their decision-making
            processes, whenever they can have a significant impact on people’s
            lives.
        \end{itemize}
    \end{itemize}

    \item \emph{Open science practices}: Describe how appropriate open science
    practices are implemented as an integral part of the proposed methodology.
    Show how the choice of practices and their implementation is adapted to the
    nature of your work in a way that will increase the chances of the project
    delivering on its objectives [e.g. up to 1/2 page, including research data
    management]. If you believe that none of these practices are appropriate for
    your project, please provide a justification here.

@@

    \item \emph{Research data management and management of other research outputs}:
    Applicants generating/collecting data and/or other research outputs (except for
    publications) during the project must explain how the data will be managed
    in line with the FAIR principles (Findable, Accessible, Interoperable,
    Reusable).

    \emph{For guidance on open science practices and research data management,
    please refer to the relevant section of the \href{https://ec.europa.eu/info/funding-tenders/opportunities/docs/2021-2027/horizon/guidance/programme-guide_horizon_en.pdf}{HE Programme Guide}
    on the Funding \& Tenders Portal.}

    Please also see the “how to evaluate open science in Horizon Europe proposals”
    video on the \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/support/videos}{Funding \& Tenders portal} and
    \href{https://rea.ec.europa.eu/open-science_en}{Open Science - European Commission (europa.eu)}.
\end{itemize}

\subsection{Quality of the supervision, training and of the two-way transfer of
    knowledge between the researcher and the host}

@@

\textbf{Supervision} is one of the crucial elements of successful research. Guiding,
supporting, directing, advising and mentoring are key factors for a researcher
to pursue his/her career path. In this context, all MSCA-funded projects are
encouraged to follow the recommendations outlined in the
\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}\footnotemark{}.

\footnotetext{While the MSCA Guidelines on Supervision are non-binding,
funded-projects are strongly encouraged to take them into account.}

\subsection{Quality and appropriateness of the researcher's professional
experience, competences and skills}

@@

\section{Impact \mscatag{IMP-ACT-IA}}
\label{IMP-ACT-IA}

\subsection{Credibility of the measures to enhance the career perspectives
and employability of the researcher and contribution to his/her skills
development}

@@

\subsection{Suitability and quality of the measures to maximise expected
outcomes and impacts, as set out in the dissemination and exploitation plan,
including communication activities \mscatag{COM-DIS-VIS-CDV}}
\label{COM-DIS-VIS-CDV}

@@

\subsection{The magnitude and importance of the project’s contribution to the
expected scientific, societal and economic impacts}

@@

\section{Quality and Efficiency of the Implementation
         \mscatag{QUA-LIT-QL} \mscatag{WRK-PLA-WP} \mscatag{CON-SOR-CS} \mscatag{PRJ-MGT-PM}}
\label{WRK-PLA-WP}

\subsection{Quality and effectiveness of the work plan, assessment of risks and
appropriateness of the effort assigned to work packages}

@@

The schedule in the Gantt chart should indicate the number of months elapsed
from the start of the action (Month 1).

\subsection{Quality and capacity of the host institutions and participating
organisations, including hosting arrangements}

@@

\begin{itemize}
    \item Hosting arrangements, including integration in the team/institution
    and support services available to the researcher.

@@

\subsection*{Associated partners linked to a beneficiary {\protect\footnotemark{}}}

>>>>

% {{{ commands

% add your own fancy commands
% \NewDocumentCommand \mycmd { m } {\textbf{#1}}

@@

% NOTE: update these as necessary
% \mscaidentifier{HORIZON-MSCA-2025-PF-01}
% \mscaproject{TDB}

@@

\section{Excellence \mscatag{REL-EVA-RE}}
\label{sc:excellence}

\subsection{Quality and pertinence of the project's research and innovation objectives
    (and the extent to which they are ambitious, and go beyond the state of the art)}
    \mscatag{QUA-LIT-QL}
\label{ssc:excellence:quality}

@@

\subsection{Soundness of the proposed methodology
    (including interdisciplinary approaches, consideration of the gender
    dimension and other diversity aspects if relevant for the research project,
    and the quality of open science practices)}
\label{ssc:excellence:methodology}

@@

@@

        \item  Sex, gender and diversity analysis refers to biological
        characteristics and social/cultural factors respectively. For guidance on
        methods of sex / gender analysis and the issues to be taken into account,
        please refer to this
        \href{https://op.europa.eu/en/publication-detail/-/publication/33b4c99f-2e66-11eb-b27b-01aa75ed71a1/language-en}{link}.
    \end{itemize}

    \item \emph{Open science practices}: Describe how appropriate open science
    practices are implemented as an integral part of the proposed methodology.
    Show how the choice of practices and their implementation is adapted to the
    nature of your work in a way that will increase the chances of the project
    delivering on its objectives \emph{[1/2 page]}. If you believe that none of
    these practices are appropriate for your project, please provide a justification
    here.

@@

    \item Proposals selected for funding under Horizon Europe will need to develop
    a detailed data management plan (DMP) for making their data/research outputs
    findable, accessible, interoperable and reusable (FAIR) as a deliverable by
    month 6 and revised towards the end of a project's lifetime. The DMP should
    describe how research outputs (especially research data) generated and/or
    collected during the project will be managed so as to ensure that they are
    findable, accessible, interoperable and reusable.

    \emph{For guidance on open science practices and research data management,
    please refer to the relevant section of the
    \href{https://ec.europa.eu/info/funding-tenders/opportunities/docs/2021-2027/horizon/temp-form/af/af_he-msca-pf_en.pdf}{HE Programme Guide}
    on the Funding \& Tenders Portal.}
\end{itemize}

\subsection{Quality of the supervision, training and of the two-way transfer of
    knowledge between the researcher and the host}
\label{ssc:excellence:supervision}

@@

\textbf{Supervision} is one of the crucial elements of successful research. Guiding,
supporting, directing, advising and mentoring are key factors for a researcher
to pursue his/her career path. In this context, all MSCA-funded projects are
encouraged to follow the recommendations outlined in the
\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}.

\subsection{Quality and appropriateness of the researcher's professional
    experience, competences and skills}
\label{ssc:excellence:researcher}

@@

\section{Impact \mscatag{IMP-ACT-IA}}
\label{sc:impact}

\subsection{Credibility of the measures to enhance the career perspectives
    and employability of the researcher and contribution to his/her skills
    development}
\label{ssc:impact:career}

@@

\subsection{Suitability and quality of the measures to maximise expected
    outcomes and impacts, as set out in the dissemination and exploitation plan,
    including communication activities \mscatag{COM-DIS-VIS-CDV}}
\label{ssc:impact:outcomes}

@@

\subsection{The magnitude and importance of the project’s contribution to the
    expected scientific, societal and economic impacts}
\label{ssc:impact:future}

@@

\section{Quality and Efficiency of the Implementation
         \mscatag{QUA-LIT-QL} \mscatag{WRK-PLA-WP} \mscatag{CON-SOR-CS} \mscatag{PRJ-MGT-PM}}
\label{sc:implementation}

\subsection{Quality and effectiveness of the work plan, assessment of risks and
    appropriateness of the effort assigned to work packages}
\label{ssc:implementation:workplan}

@@

The schedule in the Gantt chart should indicate the number of months elapsed
from the start of the action (Month 1, Month 2, etc.) but no actual dates.

\subsection{Quality and capacity of the host institutions and participating
organisations, including hosting arrangements}
\label{ssc:implementation:host}

@@

\begin{itemize}
    \item Hosting arrangements, including integration in the team/institution(s)
    and support services available to the researcher.

@@

\subsection*{Associated partners linked to a beneficiary {\protect\footnotemark{}}}
\label{ssc:implementation:partners}
